Complete Algebraic File Synchronization

### 2015-12-20 2015/def-filesystem.tex
Fixed typos
New figures

To model this, in $\setv$ we distinguish between 
file contents ($\setf$) and directory contents ($\setd$), that is,
if $\setb = \{\empt\}$ then:
\[ \setv = \setb \cup \setf \cup \setd \]
The tree propety can then be defined as
\begin{align*}
\forall n\in\setn: &\FS(n) \neq \empt \\ % TODO alignment problem
&\quad\wedge \parent(n) \neq \topnode \\
&\Rightarrow \FS(\parent(n)) \in \setd 
\end{align*}
This means that as we move down from the root of a tree of nodes,
the types of values we encounter in the filesystem can only change according to the following
transition diagram:

\input{type-transition}

>>>>

To model this, in $\setv$ we distinguish between 
file contents ($\setf$) and directory contents ($\setd$), that is,
if $\setb = \{\empt\}$ then:
\[ \setv = \setb \cup \setf \cup \setd \]
The tree property can then be defined as
\begin{align*}
\forall n\in\setn: &\FS(n) \neq \empt \\ % TODO alignment problem
&\quad\wedge \parent(n) \neq \topnode \\
&\Rightarrow \FS(\parent(n)) \in \setd 
\end{align*}
This means that as we move down from the root of a tree of nodes,
the types of values we encounter in the filesystem can only change according to the
transition diagram in \cref{fig_transition}.

\begin{figure}[htb]
\input{fig-type-transition}
\caption{Transitions between types of values in a filesystem}\label{fig_transition}
\end{figure}

### 2015-12-20 2015/works-inverse.tex
New figures

For the proposition
\[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]
the rest of the proof is illustrated by the diagram below
where Dom($x$), the domain of $x$, represents the set of filesystems
the sequence $x$ does not break, or neither of the sequences in the set $x$ breaks.

\input{inverse-works} % TODO arrows too small

>>>>

For the proposition
\[ \worksc{B\cc \seqset{A}}{\seqset{S}} \Rightarrow \worksc{\seqset{A}}{B^{-1}\cc \seqset{S}} \]
the rest of the proof is illustrated by \cref{fig_invmove}
where Dom($x$), the domain of $x$, represents the set of filesystems
the sequence $x$ does not break, or neither of the sequences in the set $x$ breaks.

\begin{figure}[htb]
\input{fig-inverse-works}
\caption{Proof of \cref{r_invmove}}\label{fig_invmove}
\end{figure}
